Ice sheet mass flows

### 2024-06-05 ms.tex
shelf text

>>>>

\subsection{Shelves}

Mass change of shelves is a bulk aggregate property, and should not the default reporting metric because it obscures information. For example, in theory ice shelf mass can grow even as they collapse, as long as the grounding line retreats (adds mass to the shelf from the upstream ice sheet) faster than the mass loss at the frontal or submarine boundaries. A mass flow diagram dedicated to ice shelves (this one is not) would clearly convey each of these processes.
